%-------------------------
% Resume in Latex
% Author : J Abhiram Reddy
% Based on: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ATS-parsable output
\pdfgentounicode=1

%----------CUSTOM COMMANDS----------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\raisebox{0.15ex}{\tiny$\bullet$}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape J Abhiram Reddy} \\ \vspace{2pt}
    \small Hyderabad, Telangana, India $|$ +91-9390712822 $|$ \href{mailto:jabhiramreddy.work@gmail.com}{\underline{jabhiramreddy.work@gmail.com}} \\ \vspace{2pt}
    \href{https://linkedin.com/in/j-abhiram-reddy}{\underline{LinkedIn}} $|$ \href{https://github.com/jabhiramreddy-code}{\underline{GitHub}} $|$ \href{https://leetcode.com/J_Abhiram_reddy/}{\underline{LeetCode}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
Software Development Engineer with 2.5+ years building and operating production systems. Inaugural engineer at a healthcare-data startup, owning Next.js/React responsive web applications, backend APIs, AWS cloud infrastructure, and HIPAA-compliant data pipelines end to end.

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: TypeScript, JavaScript, Python, SQL} \\ [2pt]
     \textbf{Frontend \& UI}{: Next.js (SSR / SSG), React, Responsive Web Design, Core Web Vitals, HTML5 / CSS3, State Management} \\[2pt]
     \textbf{Backend \& Frameworks}{: Node.js, Elysia (Bun), Express.js, FastAPI, Flask} \\[2pt]
     \textbf{Databases \& Caching}{: PostgreSQL, MongoDB, Redis, MySQL, DynamoDB} \\[2pt]
     \textbf{Cloud \& DevOps}{: AWS (ECS, ALB, EC2, S3, CloudFront, Route 53), SST (IaC), Docker, CI/CD, Linux} \\[2pt]
     \textbf{Architecture \& Security}{: REST APIs, WebSockets, Microservices, Event-Driven Architecture, HL7 FHIR, HIPAA}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer}{Feb. 2024 -- Present}
      {Vectorsoft \textnormal{\footnotesize}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Inaugural engineer — owned end-to-end software architecture, responsive frontend applications, backend APIs, cloud setup, and release engineering from prototype to production.}
        \resumeItem{Architected and shipped the responsive, high-performance customer-facing web application in \textbf{Next.js (SSR / SSG)} and \textbf{React}, optimizing Core Web Vitals and SEO while integrating via REST APIs and WebSockets.}
        \resumeItem{Designed a \textbf{multi-tenant} microservices architecture with asynchronous, event-driven message queues to guarantee data consistency across services.}
        \resumeItem{Built \textbf{HL7 FHIR} data ingestion pipelines on \textbf{AWS HealthLake}, centralizing patient records across provider systems to enable real-time population-health analytics.}
        \resumeItem{Architected the platform to meet \textbf{HIPAA} compliance: AES-256 encryption in transit and at rest, automated audit logging, PHI de-identification, and RBAC with MFA via Auth0/Okta.}
        \resumeItem{Engineered a \textbf{Redis} cache-aside layer for session metadata and hot lookups, cutting primary database load by \textbf{50\%} and holding API latency under \textbf{100ms} through peak traffic.}
        \resumeItem{Built and operate the \textbf{AWS} environment (ECS, ALB, EC2, S3, CloudFront, Route 53) with \textbf{Docker} and \textbf{SST} as infrastructure-as-code with CI/CD at \textbf{99.9\%} uptime.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Software Engineer}{Sep. 2023 -- Jan. 2024}
      {Self-Employed}{Remote}
      \resumeItemListStart
        \resumeItem{Built and deployed the backend for \textbf{openstudyai.com}, an AI-driven education platform, on a \textbf{Python/Flask} and AWS stack serving a global user base.}
        \resumeItem{Implemented rate limiting and session caching with \textbf{Redis} to keep read-heavy traffic off the primary database.}
        \resumeItem{Ran the product end to end, from wireframes to production deployment, and cut monthly AWS spend by \textbf{20\%} through right-sizing and resource cleanup.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vidya Jyothi Institute of Technology}{Hyderabad, India}
      {Bachelor of Technology in Computer Science; \textbf{CGPA: 7.99}}{Aug. 2019 -- Aug. 2023}
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \begin{itemize}[leftmargin=0.3in, label=\raisebox{0.15ex}{\tiny$\bullet$}]
    \resumeItem{Ranked \textbf{1st of 400+ participants} in the college-wide CodeKaze coding competition (2023).}
    \resumeItem{Sustained a 200-day problem-solving streak on \textbf{LeetCode}.}
  \end{itemize}\vspace{-5pt}

\end{document}
